Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-12 MUSES_vs_BYOD_solutions.tex
Quito Keywords por requisitos de la revista

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   KEYWORDS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{keyword}
Corporate mobile security \sep End-to-end security solutions \sep User-centric systems \sep Self-adaptation \sep Multi-platform \sep Security Policies \sep Data security and data privacy \sep BYOD
\end{keyword}

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   KEYWORDS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{keyword}
Corporate mobile security \sep User-centric systems \sep Self-adaptation \sep Multi-platform \sep BYOD
\end{keyword}
